Manuscript draft

### 2024-06-10 manuscript.rmd
more figures in ms

plt <- a + b + plot_layout(widths = c(4, 1))
ggsave(plot = plt, filename = here("fig/figures/degree/sp_situ.png"), width = 12, height = 6)
```

@@

plt <- a + b + plot_layout(widths = c(4, 1))
ggsave(plot = plt, filename = here("fig/figures/degree/rd_situ.png"), width = 12, height = 6)
```

@@

plt <- a + b + plot_layout(widths = c(4, 1))
ggsave(plot = plt, filename = here("fig/figures/strength/sp_situ.png"), width = 12, height = 6)
```

@@

plt <- a + b + plot_layout(widths = c(4, 1))
ggsave(plot = plt, filename = here("fig/figures/strength/rd_situ.png"), width = 12, height = 6)
```

@@

>>>>

plt <- a + b + plot_layout(widths = c(4, 1))
ggsave(plot = plt, filename = here("fig/figures/degree/deg_sp_situ.png"), width = 12, height = 6)
```

@@

plt <- a + b + plot_layout(widths = c(4, 1))
ggsave(plot = plt, filename = here("fig/figures/degree/deg_rd_situ.png"), width = 12, height = 6)
```

@@

plt <- a + b + plot_layout(widths = c(4, 1))
ggsave(plot = plt, filename = here("fig/figures/strength/str_sp_situ.png"), width = 12, height = 6)
```

@@

plt <- a + b + plot_layout(widths = c(4, 1))
ggsave(plot = plt, filename = here("fig/figures/strength/str_rd_situ.png"), width = 12, height = 6)
```

## Movement effects (non-significant)

```{r}
dataset <- as.data.frame(ggeffect(model = deg_z_mod, terms = c("movement", "situ"))) %>% mutate(group = case_when(group == "Fe" ~ "Feeding",
                                                                                                                   group == "Fl" ~ "Flight",
                                                                                                                   group == "Ro" ~ "Roosting"))

a <- ggplot(data = dataset, 
       aes(x, predicted))+
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group),
              alpha = 0.2, linewidth = 0.6, show.legend = F)+
  geom_point(data = pts,
             aes(x = movement, y = z_deg, col = group),
             pch = 1)+
  geom_line(aes(col = group), linewidth = 1)+
  facet_wrap(~group, scales = "free_y")+
  scale_color_manual(name = "Situation", values = situcolors)+
  scale_fill_manual(name = "Situation", values = situcolors)+
  ylab("Degree (z-score)")+ xlab("Movement")+
  theme(legend.position = "none",
        text = element_text(size = 16))

dat <- as.data.frame(emmeans::emtrends(deg_z_mod, specs = "situ", var = "movement")) %>% mutate(situ = case_when(situ == "Fe" ~ "Feeding",
                                                                                                                  situ == "Fl" ~ "Flight",
                                                                                                                  situ == "Ro" ~ "Roosting"))

b <- dat %>%
  ggplot(aes(x = situ, y = movement.trend, col = situ))+
  geom_point(size = 6)+
  geom_errorbar(aes(x = situ, ymin = lower.CL, ymax = upper.CL), 
                width = 0, linewidth = 2) +
  geom_hline(aes(yintercept = 0), linetype = 2)+
  scale_color_manual(values = situcolors)+ scale_x_discrete(limits = rev, position = "top")+
  coord_flip()+ ylab("Movement \neffect")+
  theme(legend.position = "none", 
        text = element_text(size = 16),
        axis.title.y = element_blank())

plt <- a + b + plot_layout(widths = c(4, 1))
ggsave(plot = plt, filename = here("fig/figures/degree/deg_mv_situ.png"), width = 12, height = 6)
```

```{r}
dataset <- as.data.frame(ggeffect(model = str_z_mod, terms = c("movement", "situ"))) %>% mutate(group = case_when(group == "Fe" ~ "Feeding",
                                                                                                                   group == "Fl" ~ "Flight",
                                                                                                                   group == "Ro" ~ "Roosting"))

a <- ggplot(data = dataset, 
       aes(x, predicted))+
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group),
              alpha = 0.2, linewidth = 0.6, show.legend = F)+
  geom_point(data = pts,
             aes(x = movement, y = z_str, col = group),
             pch = 1)+
  geom_line(aes(col = group), linewidth = 1)+
  facet_wrap(~group, scales = "free_y")+
  scale_color_manual(name = "Situation", values = situcolors)+
  scale_fill_manual(name = "Situation", values = situcolors)+
  ylab("Strength (z-score)")+ xlab("Movement")+
  theme(legend.position = "none",
        text = element_text(size = 16))

dat <- as.data.frame(emmeans::emtrends(str_z_mod, specs = "situ", var = "movement")) %>% mutate(situ = case_when(situ == "Fe" ~ "Feeding",
                                                                                                                  situ == "Fl" ~ "Flight",
                                                                                                                  situ == "Ro" ~ "Roosting"))

b <- dat %>%
  ggplot(aes(x = situ, y = movement.trend, col = situ))+
  geom_point(size = 6)+
  geom_errorbar(aes(x = situ, ymin = lower.CL, ymax = upper.CL), 
                width = 0, linewidth = 2) +
  geom_hline(aes(yintercept = 0), linetype = 2)+
  scale_color_manual(values = situcolors)+ scale_x_discrete(limits = rev, position = "top")+
  coord_flip()+ ylab("Movement \neffect")+
  theme(legend.position = "none", 
        text = element_text(size = 16),
        axis.title.y = element_blank())

plt <- a + b + plot_layout(widths = c(4, 1))
ggsave(plot = plt, filename = here("fig/figures/strength/str_mv_situ.png"), width = 12, height = 6)
```

@@

## Plots for models before accounting for explicit space use

```{r}
summary(deg_mod) # space*situ, movement*season, movement*situ, roost_div
summary(str_mod) # roost_div*situ only
```

Degree: space\*situ

```{r}
dataset <- as.data.frame(ggeffect(model = deg_mod, terms = c("space_use", "situ"))) %>% mutate(group = case_when(group == "Fe" ~ "Feeding",
                                                                                                                   group == "Fl" ~ "Flight",
                                                                                                                   group == "Ro" ~ "Roosting"))

a <- ggplot(data = dataset, 
       aes(x, predicted))+
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group),
              alpha = 0.2, linewidth = 0.6, show.legend = F)+
  geom_point(data = pts,
             aes(x = space_use, y = normDegree, col = group),
             pch = 1)+
  geom_line(aes(col = group), linewidth = 1)+
  facet_wrap(~group, scales = "free_y")+
  scale_color_manual(name = "Situation", values = situcolors)+
  scale_fill_manual(name = "Situation", values = situcolors)+
  ylab("Degree (normalized)")+ xlab("Space use")+
  theme(legend.position = "none",
        text = element_text(size = 16))

dat <- as.data.frame(emmeans::emtrends(deg_mod, specs = "situ", var = "space_use")) %>% mutate(situ = case_when(situ == "Fe" ~ "Feeding",
                                                                                                                  situ == "Fl" ~ "Flight",
                                                                                                                  situ == "Ro" ~ "Roosting"))

plt <- a + b + plot_layout(widths = c(4, 1))
ggsave(plot = plt, filename = here("fig/figures/degree/nonpermuted/np_deg_sp_situ.png"), width = 12, height = 6)
```

Degree: movement\*season

```{r}
pts_szn <- linked %>% mutate(group = season)
dataset <- as.data.frame(ggeffect(model = deg_mod, terms = c("movement", "season")))

a <- ggplot(data = dataset, 
       aes(x, predicted))+
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group),
              alpha = 0.2, linewidth = 0.6, show.legend = F)+
  geom_point(data = pts_szn,
             aes(x = movement, y = normDegree, col = group),
             pch = 1)+
  geom_line(aes(col = group), linewidth = 1)+
  facet_wrap(~group, scales = "free_y")+
  scale_color_manual(name = "Season", values = seasoncolors)+
  scale_fill_manual(name = "Season", values = seasoncolors)+
  ylab("Degree (normalized)")+ xlab("Movement")+
  theme(legend.position = "none",
        text = element_text(size = 16))

dat <- as.data.frame(emmeans::emtrends(deg_mod, specs = "season", var = "movement"))

b <- dat %>%
  ggplot(aes(x = season, y = movement.trend, col = season))+
  geom_point(size = 6)+
  geom_errorbar(aes(x = season, ymin = lower.CL, ymax = upper.CL), 
                width = 0, linewidth = 2) +
  geom_hline(aes(yintercept = 0), linetype = 2)+
  scale_color_manual(values = seasoncolors)+ scale_x_discrete(limits = rev, position = "top")+
  coord_flip()+ ylab("Movement \neffect")+
  theme(legend.position = "none", 
        text = element_text(size = 16),
        axis.title.y = element_blank())

plt <- a + b + plot_layout(widths = c(4, 1))
ggsave(plot = plt, filename = here("fig/figures/degree/nonpermuted/np_deg_mv_season.png"), width = 12, height = 6)
```

Degree: movement\*situ

```{r}
dataset <- as.data.frame(ggeffect(model = deg_mod, terms = c("movement", "situ"))) %>% mutate(group = case_when(group == "Fe" ~ "Feeding",
                                                                                                                   group == "Fl" ~ "Flight",
                                                                                                                   group == "Ro" ~ "Roosting"))

a <- ggplot(data = dataset, 
       aes(x, predicted))+
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group),
              alpha = 0.2, linewidth = 0.6, show.legend = F)+
  geom_point(data = pts,
             aes(x = movement, y = normDegree, col = group),
             pch = 1)+
  geom_line(aes(col = group), linewidth = 1)+
  facet_wrap(~group, scales = "free_y")+
  scale_color_manual(name = "Situation", values = situcolors)+
  scale_fill_manual(name = "Situation", values = situcolors)+
  ylab("Degree (normalized)")+ xlab("Movement")+
  theme(legend.position = "none",
        text = element_text(size = 16))

dat <- as.data.frame(emmeans::emtrends(deg_mod, specs = "situ", var = "movement")) %>% mutate(situ = case_when(situ == "Fe" ~ "Feeding",
                                                                                                                  situ == "Fl" ~ "Flight",
                                                                                                                  situ == "Ro" ~ "Roosting"))

b <- dat %>%
  ggplot(aes(x = situ, y = movement.trend, col = situ))+
  geom_point(size = 6)+
  geom_errorbar(aes(x = situ, ymin = lower.CL, ymax = upper.CL), 
                width = 0, linewidth = 2) +
  geom_hline(aes(yintercept = 0), linetype = 2)+
  scale_color_manual(values = situcolors)+ scale_x_discrete(limits = rev, position = "top")+
  coord_flip()+ ylab("Movement \neffect")+
  theme(legend.position = "none", 
        text = element_text(size = 16),
        axis.title.y = element_blank())

plt <- a + b + plot_layout(widths = c(4, 1))
ggsave(plot = plt, filename = here("fig/figures/degree/nonpermuted/np_deg_mv_situ.png"), width = 12, height = 6)
```

Degree: roost_div(\*situ)

```{r}
dataset <- as.data.frame(ggeffect(model = deg_mod, terms = c("roost_div", "situ"))) %>% mutate(group = case_when(group == "Fe" ~ "Feeding",
                                                                                                                   group == "Fl" ~ "Flight",
                                                                                                                   group == "Ro" ~ "Roosting"))

a <- ggplot(data = dataset, 
       aes(x, predicted))+
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group),
              alpha = 0.2, linewidth = 0.6, show.legend = F)+
  geom_point(data = pts,
             aes(x = roost_div, y = normDegree, col = group),
             pch = 1)+
  geom_line(aes(col = group), linewidth = 1)+
  facet_wrap(~group, scales = "free_y")+
  scale_color_manual(name = "Situation", values = situcolors)+
  scale_fill_manual(name = "Situation", values = situcolors)+
  ylab("Degree (normalized)")+ xlab("Roost diversification")+
  theme(legend.position = "none",
        text = element_text(size = 16))

dat <- as.data.frame(emmeans::emtrends(deg_mod, specs = "situ", var = "roost_div")) %>% mutate(situ = case_when(situ == "Fe" ~ "Feeding",
                                                                                                                  situ == "Fl" ~ "Flight",
                                                                                                                  situ == "Ro" ~ "Roosting"))

plt <- a + b + plot_layout(widths = c(4, 1))
ggsave(plot = plt, filename = here("fig/figures/degree/nonpermuted/np_deg_rd_situ.png"), width = 12, height = 6)
```

Strength: roost_div\*situ

```{r}
dataset <- as.data.frame(ggeffect(model = str_mod, terms = c("roost_div", "situ"))) %>% mutate(group = case_when(group == "Fe" ~ "Feeding",
                                                                                                                   group == "Fl" ~ "Flight",
                                                                                                                   group == "Ro" ~ "Roosting"))

a <- ggplot(data = dataset, 
       aes(x, predicted))+
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group),
              alpha = 0.2, linewidth = 0.6, show.legend = F)+
  geom_point(data = pts,
             aes(x = roost_div, y = normStrength, col = group),
             pch = 1)+
  geom_line(aes(col = group), linewidth = 1)+
  facet_wrap(~group, scales = "free_y")+
  scale_color_manual(name = "Situation", values = situcolors)+
  scale_fill_manual(name = "Situation", values = situcolors)+
  ylab("Degree (normalized)")+ xlab("Roost diversification")+
  theme(legend.position = "none",
        text = element_text(size = 16))

dat <- as.data.frame(emmeans::emtrends(str_mod, specs = "situ", var = "roost_div")) %>% mutate(situ = case_when(situ == "Fe" ~ "Feeding",
                                                                                                                  situ == "Fl" ~ "Flight",
                                                                                                                  situ == "Ro" ~ "Roosting"))

b <- dat %>%
  ggplot(aes(x = situ, y = roost_div.trend, col = situ))+
  geom_point(size = 6)+
  geom_errorbar(aes(x = situ, ymin = asymp.LCL, ymax = asymp.UCL), 
                width = 0, linewidth = 2) +
  geom_hline(aes(yintercept = 0), linetype = 2)+
  scale_color_manual(values = situcolors)+ scale_x_discrete(limits = rev, position = "top")+
  coord_flip()+ ylab("Roost diversification \neffect")+
  theme(legend.position = "none", 
        text = element_text(size = 16),
        axis.title.y = element_blank())

plt <- a + b + plot_layout(widths = c(4, 1))
ggsave(plot = plt, filename = here("fig/figures/strength/nonpermuted/np_deg_rd_situ.png"), width = 12, height = 6)
```
